### 2021-06-10 paper/medical_parameters.tex
Remove table form appendix on medical parameters.

For the time from symptom onset until need for intensive care we rely on data by the US
CDC (\citet{Stokes2020}) and \href{https://bit.ly/3yKXFyu}{the OpenABM-Project}.
Table~\ref{tab:symptomatic-to-ICU} shows our derivations for the probabilities of
requiring intensive care per age group.

\begin{table}[tb]
    \caption{Shares of symptomatic patients who will require ICU care by age groups.}
    \label{tab:symptomatic-to-ICU}
    \centering

    \begin{tabular}{ll}
        \toprule
        Age Group & Share \\
        \midrule
        0-9 & 0.00005 \\
        10-19 & 0.00030 \\
        20-29 & 0.00075 \\
        30-39 & 0.00345 \\
        40-49 & 0.01380 \\
        50-59 & 0.03404 \\
        60-69 & 0.10138 \\
        70-79 & 0.16891 \\
        80-100 & 0.26871 \\
        \bottomrule
    \end{tabular}

    \tablenotes{
        The data is taken from \citet{Stokes2020} and
        \href{https://github.com/BDI-pathogens/OpenABM-Covid19/blob/572e24ca2dbf7153789a92ad3a27e4c515d0e576/documentation/parameters/parameter_dictionary.md}{the
        OpenABM-Project}. }

\end{table}

For those who will require intensive care we follow \citet{Chen2020} who estimate the
time from symptom onset to ICU admission as 8.5 $\pm$ 4 days. This aligns well with
numbers reported for the time from first symptoms to hospitalization:
\citet{Gaythorpe2020} report a mean of 5.76 with a standard deviation of 4. This is also
in line with the duration estimates collected by
\href{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Steckbrief.html#doc13776792bodyText16}{the
Robert-Koch-Institut}. We assume that the time between symptom onset and ICU takes 4, 6,
8 or 10 days with equal probabilities. As we do not model nursing homes, do not focus on
matching deaths and do not use the number of individuals in intensive care to estimate
our parameters, these numbers are not important for our empirical results.

>>>>

For the time from symptom onset until need for intensive care we rely on data by the US
CDC (\citet{Stokes2020}) and \href{https://bit.ly/3yKXFyu}{the OpenABM-Project}.
%Table~\ref{tab:symptomatic-to-ICU} shows our derivations for the probabilities of
%requiring intensive care per age group.
%
%\begin{table}[tb]
%    \caption{Shares of symptomatic patients who will require ICU care by age groups.}
%    \label{tab:symptomatic-to-ICU}
%    \centering
%
%    \begin{tabular}{ll}
%        \toprule
%        Age Group & Share \\
%        \midrule
%        0-9 & 0.00005 \\
%        10-19 & 0.00030 \\
%        20-29 & 0.00075 \\
%        30-39 & 0.00345 \\
%        40-49 & 0.01380 \\
%        50-59 & 0.03404 \\
%        60-69 & 0.10138 \\
%        70-79 & 0.16891 \\
%        80-100 & 0.26871 \\
%        \bottomrule
%    \end{tabular}
%
%    \tablenotes{
%        The data is taken from \citet{Stokes2020} and \href{https://bit.ly/354pKTZ}{the
%        OpenABM-Project}. }
%
%\end{table}

For those who will require intensive care we follow \citet{Chen2020} who estimate the
time from symptom onset to ICU admission as 8.5 $\pm$ 4 days. This aligns well with
numbers reported for the time from first symptoms to hospitalization:
\citet{Gaythorpe2020} report a mean of 5.76 with a standard deviation of 4. This is also
in line with the duration estimates collected by \href{https://bit.ly/3gkGtaU}{the
Robert-Koch-Institut}. We assume that the time between symptom onset and ICU takes 4, 6,
8 or 10 days with equal probabilities. As we do not model nursing homes, do not focus on
matching deaths and do not use the number of individuals in intensive care to estimate
our parameters, these numbers are not important for our empirical results.
